\plaintitle

### 2016-09-22 drafts/labor/cases.tex
removed dumb paragraph

\msb{this needs a transition into it. Before you lay out our method, lay out what we're trying to do. What's our goal here? THEN the method can explain how we achieved it. This might involve switching the order of some of the text here}

We look at lots of papers that use the term ``crowdsourcing'' or ``crowd work''
in the abstracts and titles of their papers,  especially the papers that we cited earlier, to try
to answer the questions that we posed in the introduction.
Then we look to the piecework literature to see whether and to what extent
piecework answers the questions we, crowdsourcing researchers, have asked.
We then see whether and how crowdsourcing as we know it has differed from piecework,  and how that affects the predictions and conclusions made in the piecework literature.

>>>>

% \msb{this needs a transition into it. Before you lay out our method, lay out what we're trying to do. What's our goal here? THEN the method can explain how we achieved it. This might involve switching the order of some of the text here}

% We look at lots of papers that use the term ``crowdsourcing'' or ``crowd work''
% in the abstracts and titles of their papers,  especially the papers that we cited earlier, to try
% to answer the questions that we posed in the introduction.
% Then we look to the piecework literature to see whether and to what extent
% piecework answers the questions we, crowdsourcing researchers, have asked.
% We then see whether and how crowdsourcing as we know it has differed from piecework,  and how that affects the predictions and conclusions made in the piecework literature.
